msb106_assignment

### 2024-01-27 msb106_assignment.qmd
ø

```{r}
#| echo: false
maindata <- maindata %>%
  group_by(geo, TIME_PERIOD) %>%
  mutate(arb.ledig.geo.mean = mean(arbeidsledig, na.rm = TRUE), huspris.geo.mean = mean(huspris, na.rm = TRUE), arb.vekst.geo.mean = mean(arbeidsvekst, na.rm = TRUE))

@@

>>>>

```{r}
#| echo: false
maindata <- maindata %>%
  group_by(geo, TIME_PERIOD) %>%
  mutate(arb.ledig.geo.mean = mean(arbeidsledig, na.rm = TRUE), huspris.geo.mean = mean(huspris, na.rm = TRUE), arb.vekst.geo.mean = mean(arbeidsvekst, na.rm = TRUE))
```

@@

```{r}
maindata <- maindata %>%
  select(geo, deg_urb, TIME_PERIOD, OBS_VALUE, arbeidsledig, arbeidsvekst, huspris, arb.ledig.geo.mean, arb.vekst.geo.mean, huspris.geo.mean, classification_nr, classification)
```
